|

### 2017-03-21 abb_ExecSumm.Rmd
typo fix

Finally, all code used to create this analysis can be found at:  [www.github.com/andykrause/airbnbMelbourne](https://www.github.com/andykrause/airbnbMelbourne).  An interactive website that allows for deeper exploration the results is available at: [andykrause.shinyapps.io/ShouldIAirbnb](https://andykrause.shinyapps.io/ShouldIAirbnb).

>>>>

Finally, all code used to create this analysis can be found at:  [www.github.com/andykrause/airbnbMelbourne](https://www.github.com/andykrause/airbnbMelbourne).  An interactive website that allows for deeper exploration of the results is available at: [https://andykrause.shinyapps.io/ShouldIAirbnb](https://andykrause.shinyapps.io/ShouldIAirbnb).
